Extending the WebID Protocol with Access Delegation

### 2012-07-16 paper.tex
add todo notes from the telco

\usepackage[
pdftex,
bookmarks=true,
hidelinks,
unicode=true,
pdfauthor={Sebastian Tramp, Henry Story, Philipp Frischmut, Timofey Ermilov, and S\"oren Auer},
pdftitle={Extending the WebID Protocol with Access Delegation},
pdfkeywords={WebID, Social Semantic Web, Access Delegation}
]{hyperref}

@@

\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1} \and Andrei Sambra\inst{3}}

@@

@@

@@

@@

>>>>

\usepackage[
pdftex,
bookmarks=true,
hidelinks,
unicode=true,
pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Timofey Ermilov, and S\"oren Auer},
pdftitle={Extending the WebID Protocol with Access Delegation},
pdfkeywords={WebID, Social Semantic Web, Access Delegation}
]{hyperref}

@@

\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Andrei Sambra\inst{3} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1}

@@

\todo{ST: distinguish delegation of authorization vs. authentification}

@@

\todo{Sebastian Tramp: Extend it with respect to the Extended Mind paper}

@@

\section{Related Work}\label{sec:relatedwork}

\subsection{oAuth}
\todo{Andrei Sambra: Compare to oAuth}

\subsection{Cross Origin Resource Sharing (CORS)}
\todo{Henry Story: Compare to CORS in the context of Consuming Linked Data}

@@

\todo{Andrei Sambra: MyProfile description}
